### 2023-05-04 main.tex
SolutionG-Draft

@@

\cite{Sklyanin:1988yz}
\subsection{Quantum inverse scattering method}
We can apply the \textit{quantum inverse scattering method} to this process. We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We introduce the following matrices acting on the spaces with indices $a,b=0,1,\ldots,L$
\begin{equation}\label{Rmatrix}
R_{ab}(x)=\frac{(P_{ab}+Ix)}{x+1}
\begin{equation}\label{KmatrixHAT}
\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}
\begin{equation}\label{Kmatrix}
K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}
The above matrices satisfy the following equations
\begin{itemize}
\item \textit{Yang-Baxter-Equation}
R_{ab}(x-y)R_{ac}(x-z)R_{bc}(y-x)=R_{bc}(y-z)R_{ac}(x-z)R_{ab}(x-y)
\item \textit{Boundary-Yang-Baxter-Equation}
R_{ab}(x-y)\widehat{K}_{a}(x)R_{ab}(x+y)\widehat{K}_{2}(y)=\widehat{K}_{b}(y)R_{ab}(x+y)\widehat{K}_{a}(x)R_{ab}(x-y)
\item \textit{Dual Boundary-Yang-Baxter-Equation}
K_{b}(y) R_{ab}(-x-y-N) K_{a}(x)R_{ab}(y-x)=R_{ab}(y-x)K_{a}(x)R_{ab}(-x-y-N)K_{b}(y)
\end{itemize}
We define the following \textit{transfer matrix}
	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
where we used the double row monodromy
	U_{0}(x)=M_{0}(x)\widehat{K}(x)\widehat{M}_{0}(x)
	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}=R_{0L}(x)\ldots R_{01}(x)
This trasfer matrix has the following properties
	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(0))=C_{1}H+C_{2}I
with $C_{1},C_{2}>0$. \\
We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
	U_{0}(x)=\begin{pmatrix}
In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e. when the left boundary is lower triangular a end the right one is diagonal. We properly rescale them and we obtain
	\widehat{K}_{0}^{d}(x)=(1+x)\left(I+\frac{2x}{x+1}\widetilde{B}_{L}\right)=\begin{pmatrix}
		1+x&0&\ldots&0\\
		0&1-x&\ldots&0\\
		0&0&\ldots&1-x
	K_{0}^{\Delta}=\left((2x+N)\widetilde{B}_{1}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
Then we obtain the correspondent transfer matrix as
	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)

>>>>

\begin{equation}\label{HSecond}

@@

\cite{Sklyanin:1988yz}
\subsection{Quantum inverse scattering method}
We can apply the \textit{quantum inverse scattering method} to this process. We introduce the quantum space as $V=V_{1}\otimes\ldots\otimes V_{j}\otimes\ldots\otimes V_{L}$ and the auxiliary space $V_{0}$. In this specific case $V_{j}=\mathbb{C}^{N}$ $\forall j=0,1,\ldots ,L$. We introduce the following matrices acting on the spaces with indices $a,b=0,1,\ldots,L$
\begin{equation}\label{Rmatrix}
R_{ab}(x)=\frac{(P_{ab}+Ix)}{x+1}
\end{equation}
\begin{equation}\label{KmatrixHAT}
\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}
\end{equation}
\begin{equation}\label{Kmatrix}
K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}
\end{equation}
The above matrices satisfy the following equations
\begin{itemize}
\item \textit{Yang-Baxter-Equation}
\begin{equation}
R_{ab}(x-y)R_{ac}(x-z)R_{bc}(y-x)=R_{bc}(y-z)R_{ac}(x-z)R_{ab}(x-y)
\end{equation}
\item \textit{Boundary-Yang-Baxter-Equation}
\begin{equation}
R_{ab}(x-y)\widehat{K}_{a}(x)R_{ab}(x+y)\widehat{K}_{2}(y)=\widehat{K}_{b}(y)R_{ab}(x+y)\widehat{K}_{a}(x)R_{ab}(x-y)
\end{equation}
\item \textit{Dual Boundary-Yang-Baxter-Equation}
\begin{equation}
K_{b}(y) R_{ab}(-x-y-N) K_{a}(x)R_{ab}(y-x)=R_{ab}(y-x)K_{a}(x)R_{ab}(-x-y-N)K_{b}(y)
\end{equation}
\end{itemize}
We define the following \textit{transfer matrix}
\begin{equation}
	T(x)=tr_{0}\left(K_{0}(x)U_{0}(x)\right)
\end{equation}
where we used the double row monodromy
\begin{equation}
	U_{0}(x)=M_{0}(x)\widehat{K}(x)\widehat{M}_{0}(x)
\end{equation}
where 
\begin{equation}
	M_{0}(x)=R_{01}(x)\ldots R_{0L}(x)\qquad \widehat{M}_{0}=R_{0L}(x)\ldots R_{01}(x)
\end{equation}
This trasfer matrix has the following properties
\begin{equation}
	\left[T(x),T(y)\right]=0\qquad \frac{\partial}{\partial x}\log (T(0))=C_{1}H+C_{2}I
\end{equation}
with $C_{1},C_{2}>0$. \\
We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename the elements, each of them acting on the quantum space $V$, has follows
\begin{equation}
	U_{0}(x)=\begin{pmatrix}
		A(x)&B_{2}(x)&\ldots&B_{N}(x)\\
		C_{2}(x)&D_{22}(x)&\ldots&D_{2N}(x)\\
		\vdots&\vdots&\ddots&\vdots\\
		C_{N}(x)&D_{N2}(x)&\ldots&D_{NN}(x)
	\end{pmatrix}
\end{equation}
In order to carry out the mapping of non equilibrium onto equilibrium we should consider the K-matrices after the transformation \eqref{similarS}, i.e. when the left boundary is lower triangular a end the right one is diagonal. We properly rescale them and we obtain
\begin{equation}
	\widehat{K}_{0}^{d}(x)=(1+x)\left(I+\frac{2x}{x+1}\widetilde{B}_{L}\right)=\begin{pmatrix}
		1+x&0&\ldots&0\\
		0&1-x&\ldots&0\\
		\vdots&\vdots&\ddots&\vdots\\
		0&0&\ldots&1-x
	\end{pmatrix}
\end{equation}
\begin{equation}
	K_{0}^{\Delta}=\left((2x+N)\widetilde{B}_{1}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
		N+x&0&\ldots&0\\
		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\
		\vdots&\vdots&\ddots&\vdots\\
		(2x+N)(\alpha_{N}-\beta_{N})&0&\ldots&-x
	\end{pmatrix}
\end{equation}
Then we obtain the correspondent transfer matrix as
\begin{equation}
	T^{\Delta}(x)=tr_{0}\left(K_{0}^{\Delta}(x)U_{0}^{d}(x)\right)
\end{equation}
where
\begin{equation}
	U_{0}^{d}(x)=M_{0}(x)\widehat{K}_{0}^{d}(x)\widehat{M}_{0}(x)
\end{equation}
\subsection{Eigenvectors of the non equilibrium Hamiltonian}
For simplicity we first consider the case with $N=3$. We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}. For the sake of notation, we restrict to the case with $N=3$ and we denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$. The eigenvectors are the following: 
\begin{equation}
	|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\end{equation}
	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
	+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
	&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
	\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
	\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle.
We impose the powers of $\Delta_{2}\Delta_{3}$ to be equal. We obtain the following conditions 
		T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}
			B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
			B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
	\item $k_{2}\in \{0,\ldots,m_{2}\}$ and $k_{3}\in\{0,\ldots,m_{3}\}$
			&\left(G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
			\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
%	\item $k_{2}=0$ and $k_{3}\in\{1,\ldots,m_{3}\}$
	%\begin{equation}\label{cond5}
	%	\begin{split}
	%		&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
	%		=
	%		\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
	%	\end{split}
%	\end{equation}
%	\begin{equation}\label{cond6}
	%	\begin{split}
	%		&\left(T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)+B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle
	%		=
	%		\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle
	%	\end{split}
%	\end{equation}
To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1},\eqref{cond2},\eqref{cond3},\eqref{cond4}.
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{k_{2}+k_{3}}=k_{2}\}}
		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
	A_{2}= \left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
	A_{3}=\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
Therefore we rewrite \eqref{cond4} as 
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
The left-hand-side is 
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
while, on the right-hand-side we have
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}+\cdots+k_{3}}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
and similarly 
		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
Therefore,
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{k_{2}+k_{3}}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{k_{2}+k_{3}}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
We can generalize it to arbitrary number of species writing
	|\Psi_{m_{2},\ldots,m_{N}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\ldots\sum_{k_{N}=0}^{m_{n}}\Delta_{2}^{k_{2}}\cdots\Delta_{N}^{k_{N}}G_{m_{2}\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)|\Psi_{m_{N}\ldots,m_{N}}^{0}\rangle|_{\epsilon=0}
Denoting by
A_{j}=	\left\{\left((\Lambda_{m_{2}\ldots,m_{N}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{j}(x)\right\}\qquad \forall j\in \{2,\ldots,N\}
the explicit formula for $G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)$ reads
G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=&\sum_{i_{1}^{2}=0}^{1}\ldots\sum_{i_{1}^{N}=0}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{k_{2}+\cdots+k_{N}}^{q}=k_{q}\}}\right)
\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
Condition \eqref{cond4} becomes
\begin{equation}\label{cond4General}
	G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{j=2}^{N}A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)
Arguing as in the case $N=3$ we observe that 
		A_{j}G_{m_{2},\ldots,m_{N}\epsilon}^{k_{2},\ldots,k_{j}-1,\ldots,k_{N}}(x)=&\sum_{i_{1}^{j}=1}^{1}\sum_{i_{2}^{2}=0}^{1}\ldots\sum_{i_{2}^{N}=0}^{1}\ldots\sum_{i_{k_{2}+\ldots+k_{N}}^{2}=0}^{1}\ldots \sum_{i_{k_{2}+\ldots+k_{N}}^{N}=0}^{1}
	\left(\prod_{s=1}^{k_{2}+\cdots+k_{N}}\mathbbm{1}_{\{i_{s}^{2}+\cdots+i_{s}^{N}=1\}}\right)\left(\prod_{q=2}^{N}\mathbbm{1}_{\{i_{1}^{q}+\cdots+i_{k_{2}+\cdots+k_{N}}^{q}=k_{q}\}}\right)
	\prod_{s=1}^{k_{2}+\cdots+k_{N}}\prod_{q=2}^{N}A_{q}^{i_{s}^{q}}
therefore \eqref{cond4General} is fulfilled. 
We show that, if these previous conditions are satisfied, then the $|\Psi^{\Delta}_{m_{2},m_{3}}\rangle$ are indeed eigenvalues of $H^{''}$. 
\subsection{Charges}
